---
title: "Homework 5"
author: "Lincole Jiang"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(readr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


Problem 1

Since the solution has been posted and this problem ungraded, I will omit my solution here.


Problem 2

In this problem, we investigate the data posted by *The Washington Post* on homocides in 50 large U.S. cities. We first provide an overview of the dataset, create a city_state variable, before summarizing within cities to obtain the total number of homocides and the number of unsolved homocides.

```{r}
# import datset and create city_state variable
homocide <- read_csv("./data/homicide-data.csv")

# total number of homocides and unsolved homocides under each city
homocide %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>%
  group_by(city_state) %>%
  summarise(total_homocides = n(), unsolved_homocides = n(disposition == "Closed without arrest" | disposition == "Open/No arrest"))
```

First we provide an overview of the dataset. With the newly added The dataset contains `r ncol(homocide$)`

Now, for the city of Baltimode, MD, we estimate the proportion of homocides that are unsolved and save the output as an R object.
