---
title: "Homework 5"
author: "Lincole Jiang"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(readr)
library(plotly)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


Problem 1

The solution provided here closely adheres to the posted solution.


Problem 2

In this problem, we investigate the data posted by *The Washington Post* on homocides in 50 large U.S. cities. We first import the dataset and provide an overview. 

```{r}
# import datset and create city_state variable
homocide <- read_csv("./data/homicide-data.csv")
head(homocide)
```

As shown, without the added variable of city_state, the dataset contains `r ncol(homocide) - 1` variables and `r nrow(homocide)` observations. Specifically, the dataset contains the UID of the homocide victim, their first and last name, date reported, race, age, sex; city, state, and coordinates of discovery; as well as the disposition of the case. 

Now, we create a city_state variable and summarize within cities to obtain the total number of homocides and the number of unsolved homocides.

```{r}
# Create city_state variable
homocide <- homocide %>% 
  mutate(
    state = replace(state, state == "wI", "WI"),
    city_state = paste(city, state, sep = ", ")
    )

# Summarise within cities to obtain number of total cases and unsolved cases
homocide_disposition <- homocide %>% 
  group_by(city_state) %>%
  summarise(total_cases = n(), 
            unsolved_cases = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest"))

# Display results
head(homocide_disposition)
```

Now, for the city of Baltimore, MD exclusively, we run the prop.test function to estimate the proportion of homocides that are unsolved.

```{r}
# use prop.test to estimate proportions; pull test result
test_bal = homocide_disposition %>%
  filter(city_state == "Baltimore, MD") %>%
  mutate(prop_test = map2(unsolved_cases, total_cases, ~prop.test(.x, .y) %>%
                         broom::tidy())) %>% 
  unnest() %>%
  select(city_state, estimate, lower_CI = conf.low, upper_CI = conf.high)

test_bal
```

We now run this test for every city in the data set and extract the proportion and confidence interval for each.

```{r}
# Run prop.test for each city
test_full = homocide_disposition %>% 
  mutate(prop_test = map2(unsolved_cases, total_cases, ~prop.test(.x, .y) %>%
                         broom::tidy())) %>% 
  unnest() %>% #pull estimated proportion and confidence intervals
  select(city_state, estimate, lower_CI = conf.low, upper_CI = conf.high)

# Display result
head(test_full)
```

Finally, for problem 2, we create a plot that shows the estimates and the CIs for each city, while organizing the cities according to the proportion of unsolved homicides.

```{r}
scatter_ggplot = 
  test_full %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate, ymin = lower_CI, ymax = upper_CI)) +
  geom_point(alpha = 0.5) + 
  geom_errorbar()

ggplotly(scatter_ggplot)
```


### Problem 3

For this problem, 